Guarded Recursion in Agda via Sized Types

### 2019-02-04 code-oneclock-paper/latex/paper.tex
Modified conclusion

Finally, we would like to understand whether sized types can be simulated using guarded recursion.
The difficulty is representing coinductive types.
One could represent sizes by the conatural numbers, but this might not be sufficient to model infinitary coinductive types.
%%
%% Bibliography
%%

>>>>

Finally, we would like to understand whether sized types can be simulated using guarded recursion.
Sized types require dependent types and subtyping, which \GTT\ does not have.
We conjecture that Clocked Type Theory \cite{BahrGM17} can model sized types with explicit subtyping.
%%
%% Bibliography
%%
